Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Edits to intro

These mass movements would not have been possible without
efficient large-scale coordination, both physically and virtually on social
media platforms. Along with Facebook, Twitter has been credited as essential 
to the Arab Spring---both for protesters (as a means to coordinate with one 
another and to communicate with the world) and for the government response
(to monitor and track protestors to crack down on dissent) [@comninos2011twitter]. 
The events of Arab Spring have been
thoroughly discussed within the political science literature
[e.g., @lutterbeck2013arab; @koehler2017political], but to our knowledge,
the direct coupling between Syrian Twitter use and international action
has not been investigated.

@@

Just as real-world social cohesion can be
quantified, so can online cohesion. While this can be quantified in many ways,
one kind of cohesion can be found in the similarity in language use on social media.
This implicit or explicit similarity in language use can indicate shared
beliefs, thoughts, and feelings, as has been studied in research on language style
in psycholinguistics and social psychology 
[@gonzales2010language; @tausczik2010psychological; @brennan1996conceptual]; 
although previous work on language style
has often focused on individuals and small groups, this can be scaled up to examine
massive social-level changes [@michel2011quantitative; @fusaroli2015timescales]. 
This kind of massive online social cohesion can lead to real-world
social change.

@@

Social media platforms provide one way of enabling this kind of online social
cohesion by offering distributed information-gathering and real-time information
dissemination. Given its accessibility and proficiency as an information
exchange tool, Twitter has provided individuals involved in social movements
an opportunity to complement or even replace real-world social mobilization.
For example, during the 2012 Italian protests for global economic change, the riots in
Rome were mirrored by Twitter activity both on the day of the protests and in the
days following them [@vicari2013public]. Tweeting was
determined to be more effective locally in discussing real-world, real-time
events than traditional mainstream media platforms. As more and more
individuals rely on social media to obtain local news and information, it
becomes increasingly important to understand just how these micro-blogs
reflect real-world action.

## Using Nonlinear Methods to Capture Complex Relationships
Given the hypothesized interrelationship between the real-world
and online actions---and the notorious messiness of naturally occurring
data---it is critical to find appropriate analysis tools that can
identify the complex interconnections.
Traditional linear analyses have led to many notable discoveries in the
domains of psychology and political science, but time series data pose
problems that are not easily overcome with these methods. Events have
historically been conceptualized as linear chains of smaller, sequential
events with one occurrence leading to the next. 
Certain kinds of data are relatively well-suited to these analyses,
but messy, complex, variable data from real-world events can pose
challenges from overpowered samples to violation of underlying
statistical assumptions [@paxton2017finding].

At the same time, the foundational theoretical assumptions of a 
linear world has been
increasingly replaced by ideas from dynamical systems theory. Rather than
a chain of events, time series data can be thought of as nested occurrences,
where mutually constrained parts (e.g., citizens, governments, real-world
events, social media platforms) are constantly interacting, leading to
more global behaviors that are larger than the sum of the parts
[@turvey2018lectures]. Linear analyses flatten these nonlinear patterns in 
time series data and ignore the variability
that is fundamental to these systems and their evolution over time. 
However, when analyzed as dynamical systems, many phenomena
exhibit new nonlinear patterns that were formerly overlooked. 
Nonlinear methods provide means for capturing the rich temporal
dynamics and variability that unfold in time series data.

>>>>

These mass movements would not have been possible without
efficient large-scale coordination, both physically on the ground and virtually 
on social media platforms. Along with Facebook, Twitter has been credited as 
essential to the Arab Spring---both for protesters (as a means to coordinate 
with one another and to communicate with the world) and for the government 
response (to monitor and track protestors to crack down on dissent) 
[@comninos2011twitter]. The events of Arab Spring have been thoroughly 
discussed within the political science literature 
[e.g., @lutterbeck2013arab; @koehler2017political], but to our knowledge,
the direct *coupling* between Syrian Twitter cohesion and international action
coordination has not been investigated.

@@

Just as real-world social cohesion can be
quantified, so can online cohesion. While this can be quantified in many ways,
one kind of cohesion can be found in the similarity in language use on social media.
This implicit or explicit similarity in language use can indicate shared
beliefs, thoughts, and feelings, as has been studied in research on language style
in psycholinguistics and social psychology 
[@gonzales2010language; @tausczik2010psychological; @brennan1996conceptual]; 
although previous work on language style
has often focused on individuals and small groups, this can be scaled up to examine
massive social-level changes [@michel2011quantitative; @fusaroli2015timescales]. 
This kind of widespread online social cohesion can lead to real-world
social change.

@@

Social media platforms provide one way to enable this kind of online social
cohesion by offering distributed information-gathering and real-time information
dissemination. Given its accessibility and proficiency as an information
exchange tool, Twitter has provided individuals involved in social movements
an opportunity to complement or even replace real-world social mobilization.
For example, during the 2012 Italian protests for global economic change, the riots in
Rome were mirrored by Twitter activity both on the day of the protests and in the
days following them [@vicari2013public]. Tweeting was
determined to be more effective locally in discussing real-world, real-time
events than traditional mainstream media platforms. As more and more
individuals rely on social media to obtain local news and information, it
becomes increasingly important to understand just how these micro-blogs
reflect real-world action.

## Using Nonlinear Methods to Capture Complex Relationships
Given the hypothesized interrelationship between the real-world
and online actions---and the notorious messiness of naturally occurring
data---it is critical to find appropriate analysis tools that can
identify the complex interconnections. Traditional linear analyses have led to 
many notable discoveries in the domains of psychology and political science, 
but time series data pose problems that are not easily overcome with these 
methods. Events have historically been conceptualized as linear chains of 
smaller, sequential events with one occurrence leading to the next. 
Certain kinds of data are relatively well-suited to these analyses,
but messy, complex, variable data from real-world events can pose
challenges, from overpowered samples to violation of underlying
statistical assumptions [@paxton2017finding].

At the same time, the foundational theoretical assumptions of a 
linear world has been
increasingly replaced by ideas from dynamical systems theory. Rather than
a chain of events, time series data can be thought of as nested occurrences,
where mutually constrained parts (e.g., citizens, governments, real-world
events, social media platforms) are constantly interacting, leading to
more global behaviors that are larger than the sum of the parts
[@turvey2018lectures]. Linear analyses flatten time series data and ignore 
the variability that is fundamental to these systems and their evolution over 
time. However, when analyzed as dynamical systems, many phenomena
exhibit new nonlinear patterns that were formerly overlooked. 
Nonlinear methods provide means for capturing the rich temporal
dynamics and variability that unfold in time series data.

### 2020-06-01 manuscript.tex
Edits to intro

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
  pdflang={en-EN},
  pdfkeywords={social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{float}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

@@

These mass movements would not have been possible without
efficient large-scale coordination, both physically and virtually on social
media platforms. Along with Facebook, Twitter has been credited as essential
to the Arab Spring---both for protesters (as a means to coordinate with one
another and to communicate with the world) and for the government response
(to monitor and track protestors to crack down on dissent) (Comninos, 2011).
The events of Arab Spring have been
thoroughly discussed within the political science literature
(e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge,
the direct coupling between Syrian Twitter use and international action
has not been investigated.

@@

Just as real-world social cohesion can be
quantified, so can online cohesion. While this can be quantified in many ways,
one kind of cohesion can be found in the similarity in language use on social media.
This implicit or explicit similarity in language use can indicate shared
beliefs, thoughts, and feelings, as has been studied in research on language style
in psycholinguistics and social psychology
(Brennan \& Clark, 1996; Gonzales, Hancock, \& Pennebaker, 2010; Tausczik \& Pennebaker, 2010);
although previous work on language style
has often focused on individuals and small groups, this can be scaled up to examine
massive social-level changes (Fusaroli et al., 2015; Michel et al., 2011).
This kind of massive online social cohesion can lead to real-world
social change.

@@

Social media platforms provide one way of enabling this kind of online social
cohesion by offering distributed information-gathering and real-time information
dissemination. Given its accessibility and proficiency as an information
exchange tool, Twitter has provided individuals involved in social movements
an opportunity to complement or even replace real-world social mobilization.
For example, during the 2012 Italian protests for global economic change, the riots in
Rome were mirrored by Twitter activity both on the day of the protests and in the
days following them (Vicari, 2013). Tweeting was
determined to be more effective locally in discussing real-world, real-time
events than traditional mainstream media platforms. As more and more
individuals rely on social media to obtain local news and information, it
becomes increasingly important to understand just how these micro-blogs
reflect real-world action.

@@

Given the hypothesized interrelationship between the real-world
and online actions---and the notorious messiness of naturally occurring
data---it is critical to find appropriate analysis tools that can
identify the complex interconnections.
Traditional linear analyses have led to many notable discoveries in the
domains of psychology and political science, but time series data pose
problems that are not easily overcome with these methods. Events have
historically been conceptualized as linear chains of smaller, sequential
events with one occurrence leading to the next.
Certain kinds of data are relatively well-suited to these analyses,
but messy, complex, variable data from real-world events can pose
challenges from overpowered samples to violation of underlying
statistical assumptions (Paxton \& Griffiths, 2017).

At the same time, the foundational theoretical assumptions of a
linear world has been
increasingly replaced by ideas from dynamical systems theory. Rather than
a chain of events, time series data can be thought of as nested occurrences,
where mutually constrained parts (e.g., citizens, governments, real-world
events, social media platforms) are constantly interacting, leading to
more global behaviors that are larger than the sum of the parts
(Turvey, 2018). Linear analyses flatten these nonlinear patterns in
time series data and ignore the variability
that is fundamental to these systems and their evolution over time.
However, when analyzed as dynamical systems, many phenomena
exhibit new nonlinear patterns that were formerly overlooked.
Nonlinear methods provide means for capturing the rich temporal
dynamics and variability that unfold in time series data.

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{\label{table-2}CRQA results for source and target data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 25.246 & 0.001 & *** & 21.803 & 0.074 & . & 22.623 & 0.023 & *\tabularnewline
NRLINE & 75.000 & 0.000 & *** & 61.000 & 0.121 & & 64.000 & 0.038 & *\tabularnewline
maxL & 3.000 & 0.423 & & 4.000 & 0.037 & * & 3.000 & 0.370 &\tabularnewline
L & 2.053 & 0.911 & & 2.180 & 0.079 & . & 2.156 & 0.155 &\tabularnewline
ENTR & 0.208 & 0.901 & & 0.499 & 0.064 & . & 0.433 & 0.165 &\tabularnewline
rENTR & 0.300 & 0.802 & & 0.455 & 0.305 & & 0.625 & 0.032 & *\tabularnewline
LAM & 34.262 & 0.003 & ** & 30.328 & 0.016 & * & 24.098 & 0.113 &\tabularnewline
TT & 2.247 & 0.107 & & 2.176 & 0.165 & & 2.100 & 0.360 &\tabularnewline
\bottomrule
\end{longtable}

@@

@@

@@

@@

@@

\leavevmode\hypertarget{ref-vicari2013public}{}%
Vicari, S. (2013). Public reasoning around social contention: A case study of twitter use in the italian mobilization for global change. \emph{Current Sociology}, \emph{61}(4), 474--490.

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[english,man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
            pdfkeywords={social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{float}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

@@

These mass movements would not have been possible without
efficient large-scale coordination, both physically on the ground and virtually
on social media platforms. Along with Facebook, Twitter has been credited as
essential to the Arab Spring---both for protesters (as a means to coordinate
with one another and to communicate with the world) and for the government
response (to monitor and track protestors to crack down on dissent)
(Comninos, 2011). The events of Arab Spring have been thoroughly
discussed within the political science literature
(e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge,
the direct \emph{coupling} between Syrian Twitter cohesion and international action
coordination has not been investigated.

@@

Just as real-world social cohesion can be
quantified, so can online cohesion. While this can be quantified in many ways,
one kind of cohesion can be found in the similarity in language use on social media.
This implicit or explicit similarity in language use can indicate shared
beliefs, thoughts, and feelings, as has been studied in research on language style
in psycholinguistics and social psychology
(Brennan \& Clark, 1996; Gonzales, Hancock, \& Pennebaker, 2010; Tausczik \& Pennebaker, 2010);
although previous work on language style
has often focused on individuals and small groups, this can be scaled up to examine
massive social-level changes (Fusaroli et al., 2015; Michel et al., 2011).
This kind of widespread online social cohesion can lead to real-world
social change.

@@

Social media platforms provide one way to enable this kind of online social
cohesion by offering distributed information-gathering and real-time information
dissemination. Given its accessibility and proficiency as an information
exchange tool, Twitter has provided individuals involved in social movements
an opportunity to complement or even replace real-world social mobilization.
For example, during the 2012 Italian protests for global economic change, the riots in
Rome were mirrored by Twitter activity both on the day of the protests and in the
days following them (Vicari, 2013). Tweeting was
determined to be more effective locally in discussing real-world, real-time
events than traditional mainstream media platforms. As more and more
individuals rely on social media to obtain local news and information, it
becomes increasingly important to understand just how these micro-blogs
reflect real-world action.

@@

Given the hypothesized interrelationship between the real-world
and online actions---and the notorious messiness of naturally occurring
data---it is critical to find appropriate analysis tools that can
identify the complex interconnections. Traditional linear analyses have led to
many notable discoveries in the domains of psychology and political science,
but time series data pose problems that are not easily overcome with these
methods. Events have historically been conceptualized as linear chains of
smaller, sequential events with one occurrence leading to the next.
Certain kinds of data are relatively well-suited to these analyses,
but messy, complex, variable data from real-world events can pose
challenges, from overpowered samples to violation of underlying
statistical assumptions (Paxton \& Griffiths, 2017).

At the same time, the foundational theoretical assumptions of a
linear world has been
increasingly replaced by ideas from dynamical systems theory. Rather than
a chain of events, time series data can be thought of as nested occurrences,
where mutually constrained parts (e.g., citizens, governments, real-world
events, social media platforms) are constantly interacting, leading to
more global behaviors that are larger than the sum of the parts
(Turvey, 2018). Linear analyses flatten time series data and ignore
the variability that is fundamental to these systems and their evolution over
time. However, when analyzed as dynamical systems, many phenomena
exhibit new nonlinear patterns that were formerly overlooked.
Nonlinear methods provide means for capturing the rich temporal
dynamics and variability that unfold in time series data.

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{\label{table-2}CRQA results for source and target data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 25.246 & 0.001 & *** & 21.148 & 0.127 & & 22.623 & 0.023 & *\tabularnewline
NRLINE & 75.000 & 0.000 & *** & 59.000 & 0.193 & & 64.000 & 0.038 & *\tabularnewline
maxL & 3.000 & 0.423 & & 4.000 & 0.036 & * & 3.000 & 0.370 &\tabularnewline
L & 2.053 & 0.911 & & 2.186 & 0.060 & . & 2.156 & 0.155 &\tabularnewline
ENTR & 0.208 & 0.901 & & 0.510 & 0.047 & * & 0.433 & 0.165 &\tabularnewline
rENTR & 0.300 & 0.802 & & 0.464 & 0.255 & & 0.625 & 0.032 & *\tabularnewline
LAM & 34.262 & 0.003 & ** & 27.705 & 0.035 & * & 24.098 & 0.113 &\tabularnewline
TT & 2.247 & 0.107 & & 2.195 & 0.156 & & 2.100 & 0.360 &\tabularnewline
\bottomrule
\end{longtable}

@@

\hypertarget{implications}{%
\subsection{Implications}\label{implications}}

\hypertarget{implications-for-methodology}{%
\subsubsection{Implications for Methodology}\label{implications-for-methodology}}

Nonlinear methods have been transformative for a variety of research
areas (including psychology, Coco \& Dale, 2014). One of the goals in the
present work was to introduce variants of one kind of nonlinear
method---specifically, recurrence quantification analysis---to
this research area. While a number of excellent guides can provide
detailed explanations of the methods and their statistical underpinnings
(e.g., Riley \& Van Orden, 2005; Webber Jr \& Zbilut, 1994, 2005),
one of the most important considerations that should be briefly
summarized here is about data.

Nonlinear methods---including recurrence-based analyses---require
time series data. This requires repeated observations of the behavior
at interest, preferably at a frequency that provides information
about timing at a temporal resolution that allows the researcher to
make observations about interesting variations over time. While
this is easily controlled by scientists who conduct experimental
research, it can be more difficult for scientists who rely on
trace data or naturally occurring data. However, where possible,
we recommend political scientists work to expand efforts for
improving the temporal granularity of the data. One possible
means of achieving this may be through collaborative efforts
like the Open Event Data Alliance (Schrodt, Beieler, \& Idris, 2014).

\hypertarget{implications-for-theory}{%
\subsubsection{Implications for Theory}\label{implications-for-theory}}

(This would be where Leah should update her part.)

@@

\leavevmode\hypertarget{ref-coco2014cross}{}%
Coco, M. I., \& Dale, R. (2014). Cross-recurrence quantification analysis of categorical and continuous time series: An r package. \emph{Frontiers in Psychology}, \emph{5}, 510.

@@

\leavevmode\hypertarget{ref-riley2005tutorials}{}%
Riley, M. A., \& Van Orden, G. C. (Eds.). (2005). \emph{Tutorials in contemporary nonlinear methods for the behavioral sciences}. National Science Foundation.

@@

\leavevmode\hypertarget{ref-schrodt2014three}{}%
Schrodt, P. A., Beieler, J., \& Idris, M. (2014). Three's a charm?: Open event data coding with EL:DIABLO, PETRARCH, and the Open Event Data Alliance. In \emph{International studies association annual convention}.

@@

\leavevmode\hypertarget{ref-vicari2013public}{}%
Vicari, S. (2013). Public reasoning around social contention: A case study of Twitter use in the Italian mobilization for global change. \emph{Current Sociology}, \emph{61}(4), 474--490.
